---
output:
  html_document: default
  pdf_document: default
---
```yaml
---
title: "Group20_STA3005_Project"
author:
  - "Wu, Yanyi (122090587)"
  - "Shi, Jingxuan (121090479)"
  - "Wu, Yimou (121090617)"
date: "Started from Apr 2, 2025"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```

```{r setup, include=FALSE}
# --------------------------------------------------------------------------
# Global Options
# --------------------------------------------------------------------------
knitr::opts_chunk$set(echo = TRUE, 
                      cache = TRUE, 
                      autodep = TRUE,
                      cache.comments = TRUE)
```

# Introduction

This R Markdown document outlines our **R Package Proposal: Pokémon** based on the guidelines from *Package Guideline 2025*. Our package is tentatively named **`PokemonAnalysis`** and aims to provide a data analysis toolkit that explores relationships between Pokémon’s physical attributes and their combat abilities, using the open-source **`pokemon.csv`** dataset. 

The main objectives include:

1. Building classification models to identify legendary Pokémon.  
2. Analyzing correlations between height, weight, and various base stats (HP, Attack, Defense, Speed, etc.).  
3. Investigating which factors (type, stats, etc.) influence experience growth and egg steps.  
4. Evaluating strengths and weaknesses across different Pokémon types.  
5. Determining which types/patterns are most likely to be legendary.  
6. Constructing a “dream team” of six Pokémon optimized for maximum damage and balanced defense.  

We follow the instructions to meet the grading criteria (proposal, completeness, vignettes) while incorporating the recommended development workflow and “no errors/warnings” automated checking.

---

# Dataset Overview

Our dataset, **`pokemon.csv`**, contains information on 802 Pokémon from all seven generations:

- **name**: English name of the Pokémon  
- **japanese_name**: Original Japanese name  
- **pokedex_number**: National Pokédex number  
- **percentage_male**: Percentage of the species that are male (blank if genderless)  
- **type1**, **type2**: Primary and secondary Pokémon types  
- **classification**: Sun and Moon Pokédex classification text  
- **height_m**, **weight_kg**: Physical stats for height (m) and weight (kg)  
- **capture_rate**, **base_egg_steps**: Numerical measures for capture difficulty and egg hatching steps  
- **abilities**: List of possible abilities  
- **experience_growth**, **base_happiness**: Growth and happiness statistics  
- **against_* columns**: Eighteen columns for how much damage is taken from each attack type (e.g., *against_bug*, *against_dark*, etc.)  
- **hp, attack, defense, sp_attack, sp_defense, speed**: Base stats for combat  
- **generation**: Generation introduced (1 to 7)  
- **is_legendary**: Boolean indicator (legendary or non-legendary)  

Below is a quick demonstration of loading the data and performing an exploratory overview.

```{r data-overview}
suppressPackageStartupMessages(library(dplyr))

pokemon <- read.csv("pokemon.csv", stringsAsFactors = FALSE)

# Quick peek at the dataset structure
summary(pokemon[, c("name", "type1", "type2", "hp", "attack", "defense", "speed", "is_legendary")])
head(pokemon)
```

We confirm that columns such as **hp**, **attack**, **defense**, and **speed** are numerical, while **type1**, **type2**, and **is_legendary** are useful categorical fields for classification tasks.

---

# Proposed R Package Structure

Following the *Package Guideline 2025*, we plan to include:

1. **DESCRIPTION** (draft already present)  
   - Contains package metadata, authorship, version, license (MIT), and other fields.

2. **R code** (at least 8 functions)  
   - Each function addresses a different aspect of Pokémon analysis:
     1. `classify_legendary()`: Logistic model or random forest to predict `is_legendary`.  
     2. `correlate_stats()`: Correlation analysis between physical attributes and base stats.  
     3. `analyze_experience()`: Investigate experience growth and influences (e.g., type, generation).  
     4. `egg_steps_factors()`: Model the relationship between `base_egg_steps`, stats, and type.  
     5. `strength_weakness_table()`: Summarize damage multipliers vs. type1/type2.  
     6. `dream_team_builder()`: Select top 6 Pokémon to form a balanced team.  
     7. `plot_base_stats()`: Visualize distributions (e.g., boxplots, scatter plots).  
     8. `predictive_test()`: Automated check with testthat on classification performance.  

3. **Vignettes** (at least 2)  
   1. **`UsingPokemonAnalysis.Rmd`**: Comprehensive tutorial on reading data, running classification, visualizing results, building a team.  
   2. **`InDepthInsights.Rmd`**: Explores advanced analyses such as synergy among type combos, partial dependence plots for legendary classification, etc.  

4. **Data set**  
   - Bundled within the package as `data("pokemon")` or loaded externally from CSV.

5. **Automated tests** (`testthat`)  
   - Key output tests for classification accuracy, correlation checks, dimension correctness, and defensive coding.

We will strive to pass `R CMD check` with **no errors and no warnings** by properly documenting code (roxygen2), ensuring the package structure is consistent with CRAN standards, and providing examples in each function-level help file.

---

# Example Function Definitions

Below are prototypes for some of the planned functions:

```{r function-prototypes, eval=TRUE}
#' Classify Legendary Pokemon
#'
#' This function trains a simple classifier (logistic regression or random forest)
#' to predict whether a Pokemon is legendary.
#'
#' @param data A data frame of Pokemon data
#' @return A trained model object
#' @export
classify_legendary <- function(data) {
  # Basic logistic regression example
  # We'll treat is_legendary as a factor for classification.
  df <- data %>%
    filter(!is.na(is_legendary)) %>%
    mutate(isLegendary = factor(is_legendary, levels = c(0,1)))

  # For illustration, use a logistic model with key numeric predictors
  fit <- glm(isLegendary ~ hp + attack + defense + speed,
             data = df, family = binomial)
  return(fit)
}


```

```{r Code_for_correlate_stats_function ..., eval=TRUE}

#' Correlate Stats
#'
#' Compute correlations between critical numeric variables (height, weight, HP, etc.)
#'
#' @param data A data frame of Pokemon data
#' @return A correlation matrix
#' @export
correlate_stats <- function(data) {
  numeric_cols <- c("height_m", "weight_kg", "hp", "attack", "defense",
                    "sp_attack", "sp_defense", "speed")
  df <- data[, numeric_cols]
  return(cor(df, use="complete.obs"))
}

```

```{r Code_for_dream_team_builder, eval=TRUE}

#' Dream Team Builder
#'
#' Select six Pokemon to form a balanced team that maximizes a simple composite of
#' offense (attack + sp_attack) and defense (defense + sp_defense).
#'
#' @param data A data frame of Pokemon data
#' @return A tibble/data.frame of six recommended Pokemon
#' @export
dream_team_builder <- function(data) {
  data <- data %>%
    mutate(offense_score = attack + sp_attack,
           defense_score = defense + sp_defense,
           total_score = offense_score + defense_score) %>%
    arrange(desc(total_score))
  
  # For simplicity, pick top 6
  return(head(data, 6))
}
```
These examples demonstrate a subset of the planned functionalities. Each function will be fully documented using **roxygen2** tags and tested.

---

# Demonstration of Key Analyses

In this section, we illustrate a few example analyses **directly in R Markdown**. Eventually, we will migrate them into package vignettes.

## 1. Legendary Classification (Logistic Model)

```{r class-example, eval=FALSE}
# Example usage
model_legendary <- classify_legendary(pokemon)
summary(model_legendary)
```

## 2. Correlation Among Stats

```{r cor-example, eval=TRUE}
cors <- correlate_stats(pokemon)
knitr::kable(round(cors, 2), caption = "Correlation Matrix Among Key Stats")
```

## 3. Visualizing HP vs. Attack

Using **ggplot2** to illustrate some data visualization:

```{r ggplot-example, echo=TRUE}
library(ggplot2)

ggplot(pokemon, aes(x = hp, y = attack, color = factor(is_legendary))) +
  geom_point(alpha = 0.7) +
  theme_minimal(base_size = 13) +
  labs(
    title = "HP vs. Attack by Legendary Status",
    x = "HP",
    y = "Attack",
    color = "Legendary"
  )
```

---

# Testing and Checks

According to the guidelines, we must define automated tests. Our group will use [**`testthat`**](https://testthat.r-lib.org/) to ensure key functions behave correctly:

1. **Output Validity**: Functions return correct object classes.  
2. **Accuracy**: Classification passes at least a baseline threshold (e.g., 75% on a test set).  
3. **Data Dimensions**: Checking for missing columns, NAs, etc.  

Below is a simplified outline of a test file `test-classify_legendary.R`:


```{r}
# Load necessary libraries
library(assertthat)
library(dplyr)

# Load the CSV file
pokemon <- read.csv("pokemon.csv", stringsAsFactors = FALSE)

# Example test
fit <- classify_legendary(pokemon)

# Assert the object is of class glm
assert_that(inherits(fit, "glm"))
```





---

# Conclusion and Learned Points for the first part

This package, **PokemonAnalysis**, highlights the power of R packages for data science tasks:

1. **R Package Infrastructure**: Using `devtools`, `usethis`, and `roxygen2` to manage development.  
2. **Pipe Operator**: Efficient chaining of transformations with `%>%`.  
3. **Tidyverse**: Seamless data manipulation using **dplyr** and data visualization using **ggplot2**.  
4. **Automated Testing**: Ensuring reliability with **testthat**.  
5. **Documentation**: Clear roxygen-based documentation helps future users.  
6. **Modular Design**: Breaking tasks into separate functions.  
7. **Reproducibility**: Vignettes as dynamic, reproducible reports.  
8. **Real-World Relevance**: Familiar Pokémon dataset used to demonstrate classification, correlation, and advanced R workflows.


---

# Vignette Plan

We will create **two main vignettes**:

1. **`UsingPokemonAnalysis.Rmd`**  
   - Demonstrates reading the `pokemon` data, applying each function (classification, correlation, dream-team building).  
   - Shows example data transformations with the pipe operator (`%>%`).  
   - Concludes with additional plots comparing base stats across generations.

2. **`InDepthInsights.Rmd`**  
   - Explores synergy among types, legendary-likelihood predictions, and partial dependence for classification.  
   - Emphasizes advanced usage and tips gleaned from *Statistics Computing* methods (like vectorization, code efficiency).  
   
---



# Implementation
# Vignette: UsingPokemonAnalysis.Rmd

This vignette demonstrates how to use the `PokemonAnalysis` package to perform various analyses on the Pokémon dataset, including reading the data, applying functions for classification, correlation analysis, dream-team building, and visualizing results.

## Installation

First, ensure that you have installed the `PokemonAnalysis` package. Since this is a hypothetical package for the purpose of this project, we'll assume that the functions are defined within this R Markdown file for demonstration purposes.

```{r installation, eval=FALSE}
# Install the package (not applicable here)
# install.packages("PokemonAnalysis")
```

## Loading Required Libraries

We begin by loading the necessary libraries.

```{r load-libraries}
library(dplyr)
library(ggplot2)
library(knitr)
library(assertthat)

# If the functions are part of a package, load the package
# library(PokemonAnalysis)

# For demonstration, we will define the functions here
```

## Reading the Pokémon Data

We read the `pokemon.csv` dataset into R.

```{r read-data}
pokemon <- read.csv("pokemon.csv", stringsAsFactors = FALSE)

# Quick peek at the data
head(pokemon)
```

## Function Definitions

### Function: `classify_legendary`

We define the `classify_legendary` function to train a logistic regression model predicting whether a Pokémon is legendary.

```{r define-classify-legendary}
classify_legendary <- function(data) {
  df <- data %>%
    filter(!is.na(is_legendary)) %>%
    mutate(isLegendary = factor(is_legendary, levels = c(0, 1)))

  fit <- glm(isLegendary ~ hp + attack + defense + speed,
             data = df, family = binomial)
  return(fit)
}
```

### Function: `correlate_stats`

We define the `correlate_stats` function to compute correlations among key statistics.

```{r define-correlate-stats}
correlate_stats <- function(data) {
  numeric_cols <- c("height_m", "weight_kg", "hp", "attack", "defense",
                    "sp_attack", "sp_defense", "speed")
  df <- data[, numeric_cols]
  return(cor(df, use = "complete.obs"))
}
```

### Function: `dream_team_builder`

We define the `dream_team_builder` function to select a top team of six Pokémon based on combined offensive and defensive scores.

```{r define-dream-team-builder}
dream_team_builder <- function(data) {
  data <- data %>%
    mutate(offense_score = attack + sp_attack,
           defense_score = defense + sp_defense,
           total_score = offense_score + defense_score) %>%
    arrange(desc(total_score))

  # Return the top 6 Pokémon
  return(head(data, 6))
}
```

## Applying Functions

### 1. Classifying Legendary Pokémon

We apply the `classify_legendary` function to our data and examine the model summary.

```{r apply-classify-legendary}
# Train the model
model_legendary <- classify_legendary(pokemon)

# View the summary of the model
summary(model_legendary)
```

The summary shows the coefficients of the logistic regression model, indicating which statistics are significant predictors of legendary status.

### 2. Correlation Analysis

We compute the correlation matrix among key stats using `correlate_stats`.

```{r apply-correlate-stats}
cors <- correlate_stats(pokemon)

# Display the correlation matrix
knitr::kable(round(cors, 2), caption = "Correlation Matrix Among Key Stats")
```

The correlation matrix reveals relationships between physical attributes and combat stats, aiding in understanding how different variables interact.

### 3. Building a Dream Team

We use the `dream_team_builder` function to select a top team of Pokémon.

```{r apply-dream-team-builder}
dream_team <- dream_team_builder(pokemon)

# Display the dream team
knitr::kable(dream_team[, c("name", "type1", "type2", "total_score")], caption = "Dream Team of Pokémon")
```

This team consists of Pokémon with the highest combined offensive and defensive capabilities.

## Data Transformations with the Pipe Operator `%>%`

The `dplyr` package allows for seamless data transformations using the pipe operator. Here is an example of filtering and summarizing data.

```{r data-transformations}
# Calculate average stats for each type
avg_stats_by_type <- pokemon %>%
  group_by(type1) %>%
  summarise(
    avg_hp = mean(hp, na.rm = TRUE),
    avg_attack = mean(attack, na.rm = TRUE),
    avg_defense = mean(defense, na.rm = TRUE),
    avg_speed = mean(speed, na.rm = TRUE)
  ) %>%
  arrange(desc(avg_attack))

# Display the result
knitr::kable(avg_stats_by_type, caption = "Average Stats by Primary Type")
```

## Visualizations

### Plotting Base Stats Across Generations

We conclude with additional plots comparing base stats across generations.

```{r plot-base-stats}
ggplot(pokemon, aes(x = generation, y = attack)) +
  geom_boxplot() +
  theme_minimal() +
  labs(
    title = "Distribution of Attack Stats Across Generations",
    x = "Generation",
    y = "Attack"
  )
```

### HP vs. Defense Colored by Legendary Status

```{r plot-hp-defense}
ggplot(pokemon, aes(x = hp, y = defense, color = factor(is_legendary))) +
  geom_point(alpha = 0.7) +
  theme_minimal() +
  labs(
    title = "HP vs. Defense by Legendary Status",
    x = "HP",
    y = "Defense",
    color = "Legendary"
  )
```

---

# Vignette: InDepthInsights.Rmd

In this vignette, we delve deeper into advanced analyses, exploring the synergy among Pokémon types, legendary-likelihood predictions, and applying advanced statistical methods like partial dependence plots.

## Loading Required Libraries

We begin by loading necessary libraries and defining any additional functions.

```{r load-libraries-advanced}
library(dplyr)
library(ggplot2)
library(randomForest)
library(caret)
# library(ggpubr)
# For partial dependence plots
library(pdp)
```

## Reading the Pokémon Data

```{r read-data-advanced}
pokemon <- read.csv("pokemon.csv", stringsAsFactors = FALSE)
```

## Exploring Synergy Among Types

We investigate the combinations of primary and secondary types and how they relate to overall stats.

```{r type-synergy}
# Count number of Pokémon for each type combination
type_combinations <- pokemon %>%
  count(type1, type2, sort = TRUE)

# Display top type combinations
knitr::kable(head(type_combinations, 10), caption = "Top Type Combinations")
```

### Analysis of Type Combination Strength

```{r type-combination-strength}
type_stats <- pokemon %>%
  group_by(type1, type2) %>%
  summarise(
    average_total = mean(hp + attack + defense + sp_attack + sp_defense + speed, na.rm = TRUE),
    count = n(),
    .groups = "drop"
  ) %>%
  arrange(desc(average_total))

# Display top 10 type combinations by average total stats
knitr::kable(head(type_stats, 10), caption = "Strongest Type Combinations by Average Total Stats")
```

## Legendary Likelihood Predictions Using Random Forest

We build a more advanced classifier using a random forest to predict legendary status.

### Preparing the Data

```{r prepare-data-rf}
# Clean and prepare the data
df <- pokemon %>%
  filter(!is.na(is_legendary)) %>%
  select(hp, attack, defense, sp_attack, sp_defense, speed, type1, type2, is_legendary) %>%
  mutate(
    isLegendary = factor(is_legendary),
    type1 = as.factor(type1),
    type2 = as.factor(type2)
  )
```

### Training a Random Forest Model

```{r train-rf-model}
set.seed(123) # For reproducibility

# Split data into training and testing sets
trainIndex <- createDataPartition(df$isLegendary, p = .7, list = FALSE)
trainData <- df[trainIndex, ]
testData <- df[-trainIndex, ]

# Train the random forest model
rf_model <- randomForest(isLegendary ~ ., data = trainData, importance = TRUE)

# View model summary
print(rf_model)
```

### Evaluating the Model

```{r evaluate-rf-model}
# Predict on test data
predictions <- predict(rf_model, newdata = testData)

# Confusion matrix
conf_mat <- confusionMatrix(predictions, testData$isLegendary)
print(conf_mat)
```

The high accuracy and kappa statistic indicate a strong model performance.

### Variable Importance

```{r variable-importance}
# Variable importance plot
varImpPlot(rf_model, main = "Variable Importance in Predicting Legendary Status")
```

### Partial Dependence Plots

We examine how individual variables affect the probability of being legendary.

```{r partial-dependence}
# For example, partial dependence of attack
pdp_attack <- partial(rf_model, pred.var = "attack", grid.resolution = 10)
autoplot(pdp_attack) + ggtitle("Partial Dependence of Attack on Legendary Status")
```

Repeat for other important variables as desired.

## Advanced Tips for Statistical Computing

### Vectorization and Code Efficiency

We showcase how vectorized operations in R can greatly improve computational efficiency.

```{r vectorization-example}
# Inefficient approach
system.time({
  slow_result <- rep(NA, nrow(pokemon))
  for (i in 1:nrow(pokemon)) {
    slow_result[i] <- pokemon$attack[i] + pokemon$defense[i]
  }
})

# Efficient vectorized approach
system.time({
  fast_result <- pokemon$attack + pokemon$defense
})

# Check that results are equivalent
all.equal(slow_result, fast_result)
```

The vectorized approach is significantly faster, demonstrating the importance of applying vectorization in R code.


---

# Analyze-type Function Definitions and Usage
The Implementation of 'analyze_experience()', 'egg_steps_factors()', 'strength_weakness_table()', 'plot_base_stats()', 'predictive_test()'.

## 4. `analyze_experience()`

**Description**: Investigate experience growth and its influences, such as type and generation.

### Function Definition

```{r}
#' Analyze Experience Growth
#'
#' This function models the relationship between experience growth and various factors
#' such as type and generation using linear regression.
#'
#' @param data A data frame of Pokémon data
#' @return A list containing the linear model and a summary
#' @export
analyze_experience <- function(data) {
  # Ensure necessary columns are available
  required_cols <- c("experience_growth", "type1", "generation")
  if (!all(required_cols %in% names(data))) {
    stop("Data must contain 'experience_growth', 'type1', and 'generation' columns")
  }
  
  # Clean and prepare the data
  df <- data %>%
    filter(!is.na(experience_growth)) %>%
    mutate(
      type1 = as.factor(type1),
      generation = as.factor(generation)
    )
  
  # Fit a linear model
  fit <- lm(experience_growth ~ type1 + generation, data = df)
  
  return(list(model = fit, summary = summary(fit)))
}
```

### Usage and Validation

```{r}
# Apply the function
experience_analysis <- analyze_experience(pokemon)

# View the summary of the linear model
print(experience_analysis$summary)
```

**Interpretation**:

- The summary provides coefficients for each type and generation.
- Significant p-values indicate factors that significantly influence experience growth.

### Visualization

Let's visualize the average experience growth by primary type.

```{r}
# Calculate average experience growth by type
avg_exp_by_type <- pokemon %>%
  group_by(type1) %>%
  summarise(avg_experience = mean(experience_growth, na.rm = TRUE)) %>%
  arrange(desc(avg_experience))

# Plotting
ggplot(avg_exp_by_type, aes(x = reorder(type1, -avg_experience), y = avg_experience)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme_minimal() +
  labs(
    title = "Average Experience Growth by Type",
    x = "Primary Type",
    y = "Average Experience Growth"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

**Explanation**:

- The bar chart displays which types have higher or lower average experience growth.
- Types with higher bars are associated with Pokémon that generally require more experience to level up.

---

## 5. `egg_steps_factors()`

**Description**: Model the relationship between `base_egg_steps`, stats, and type.

### Function Definition

```{r}
#' Egg Steps Factors Analysis
#'
#' This function models the relationship between base egg steps and various factors
#' such as base stats and type.
#'
#' @param data A data frame of Pokémon data
#' @return A list containing the linear model and a summary
#' @export
egg_steps_factors <- function(data) {
  # Ensure necessary columns are available
  required_cols <- c("base_egg_steps", "type1", "hp", "attack", "defense", "sp_attack", "sp_defense", "speed")
  if (!all(required_cols %in% names(data))) {
    stop("Data must contain 'base_egg_steps', 'type1', and base stats columns")
  }
  
  # Clean and prepare the data
  df <- data %>%
    filter(!is.na(base_egg_steps)) %>%
    mutate(
      type1 = as.factor(type1)
    )
  
  # Base stats total
  df$stat_total <- df$hp + df$attack + df$defense + df$sp_attack + df$sp_defense + df$speed
  
  # Fit a linear model
  fit <- lm(base_egg_steps ~ stat_total + type1, data = df)
  
  return(list(model = fit, summary = summary(fit)))
}
```

### Usage and Validation

```{r}
# Apply the function
egg_steps_analysis <- egg_steps_factors(pokemon)

# View the summary of the linear model
print(egg_steps_analysis$summary)
```

**Interpretation**:

- The summary indicates how stats and types affect the number of steps required to hatch an egg.
- Significant coefficients suggest that certain stats or types have a measurable impact on egg steps.

### Visualization

Visualize the relationship between base egg steps and total base stats.

```{r}
ggplot(pokemon, aes(x = hp + attack + defense + sp_attack + sp_defense + speed, y = base_egg_steps)) +
  geom_point(alpha = 0.7) +
  theme_minimal() +
  labs(
    title = "Base Egg Steps vs. Total Base Stats",
    x = "Total Base Stats",
    y = "Base Egg Steps"
  )
```

**Explanation**:

- This scatter plot helps visualize whether there's a correlation between a Pokémon's total stats and the number of steps required for its egg to hatch.
- A trend line can be added to assess the relationship more clearly:

```{r}
geom_smooth(method = "lm", se = FALSE, color = "red")
```

---

## 6. `strength_weakness_table()`

**Description**: Summarize damage multipliers against each type based on `type1` and `type2`.

### Function Definition

```{r}
#' Strength and Weakness Table
#'
#' This function summarizes the average damage multipliers against each Pokémon
#' based on their primary and secondary types.
#'
#' @param data A data frame of Pokémon data
#' @return A data frame summarizing strengths and weaknesses
#' @export
strength_weakness_table <- function(data) {
  # Select relevant columns
  against_cols <- grep('^against_', names(data), value = TRUE)
  required_cols <- c('name', 'type1', 'type2', against_cols)
  
  df <- data[, required_cols]
  
  # Melt data to long format
  library(tidyr)
  
  df_long <- df %>%
    pivot_longer(
      cols = starts_with('against_'),
      names_to = 'against_type',
      names_prefix = 'against_',
      values_to = 'multiplier'
    )
  
  # Summarize multipliers by type1 and type2
  summary_table <- df_long %>%
    group_by(type1, type2, against_type) %>%
    summarise(
      avg_multiplier = mean(multiplier, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(type1, type2, against_type)
  
  return(summary_table)
}
```

### Usage and Validation

```{r}
# Apply the function
strength_weakness <- strength_weakness_table(pokemon)

# View a portion of the table
head(strength_weakness)
```

**Interpretation**:

- The table shows how effective attacks of different types are against Pokémon of various type combinations.
- An `avg_multiplier` greater than 1 indicates a weakness, while less than 1 indicates resistance.

### Visualization

Create a heatmap of average multipliers for a specific primary type.
```{r}
table(strength_weakness$type1, useNA = "ifany")
table(strength_weakness$type2, useNA = "ifany")

# 检查数据框
# print(fire_weakness)

# 查看行数
# nrow(fire_weakness)
```

```{r}
# Filter for primary type, e.g., 'Fire'
fire_weakness <- strength_weakness %>%
  filter(type1 == 'fire')

# Plot heatmap
ggplot(fire_weakness, aes(x = against_type, y = avg_multiplier)) +
  geom_bar(stat = "identity", fill = "orange") +
  theme_minimal() +
  labs(
    title = "Average Damage Multiplier Against Fire Type",
    x = "Attack Type",
    y = "Average Multiplier"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

**Explanation**:

- The bar chart illustrates the Fire type's strengths and weaknesses against different attack types.
- This helps in understanding which attacks are most effective against Fire-type Pokémon.

---

## 7. `plot_base_stats()`

**Description**: Visualize distributions of base stats using boxplots and scatter plots.

### Function Definition

```{r}
#' Plot Base Stats Distribution
#'
#' This function creates various plots to visualize the distribution of base stats.
#' It can generate boxplots and scatter plots for selected stats.
#'
#' @param data A data frame of Pokémon data
#' @param stat1 The first stat to plot (e.g., 'hp')
#' @param stat2 The second stat to plot if creating a scatter plot (e.g., 'attack')
#' @param plot_type The type of plot ('boxplot' or 'scatter')
#' @return A ggplot object
#' @export
plot_base_stats <- function(data, stat1, stat2 = NULL, plot_type = 'boxplot') {
  # Ensure stats are valid
  valid_stats <- c('hp', 'attack', 'defense', 'sp_attack', 'sp_defense', 'speed')
  if (!(stat1 %in% valid_stats)) {
    stop(paste("stat1 must be one of:", paste(valid_stats, collapse = ', ')))
  }
  if (!is.null(stat2) && !(stat2 %in% valid_stats)) {
    stop(paste("stat2 must be one of:", paste(valid_stats, collapse = ', ')))
  }
  
  if (plot_type == 'boxplot') {
    p <- ggplot(data, aes_string(x = 'generation', y = stat1)) +
      geom_boxplot() +
      theme_minimal() +
      labs(
        title = paste('Distribution of', toupper(stat1), 'Across Generations'),
        x = 'Generation',
        y = toupper(stat1)
      )
  } else if (plot_type == 'scatter' && !is.null(stat2)) {
    p <- ggplot(data, aes_string(x = stat1, y = stat2, color = 'factor(is_legendary)')) +
      geom_point(alpha = 0.7) +
      theme_minimal() +
      labs(
        title = paste(toupper(stat1), 'vs.', toupper(stat2), 'by Legendary Status'),
        x = toupper(stat1),
        y = toupper(stat2),
        color = 'Legendary'
      )
  } else {
    stop("Invalid plot_type or missing stat2 for scatter plot")
  }
  
  return(p)
}
```

### Usage and Validation

**Example 1: Boxplot of HP across Generations**

```{r}
# Generate boxplot
p1 <- plot_base_stats(pokemon, stat1 = 'hp', plot_type = 'boxplot')

# Display the plot
print(p1)
```

**Interpretation**:

- The boxplot shows how HP varies across different generations.
- It can highlight trends such as whether newer generations have Pokémon with higher HP.

**Example 2: Scatter Plot of Attack vs. Defense**

```{r}
# Generate scatter plot
p2 <- plot_base_stats(pokemon, stat1 = 'attack', stat2 = 'defense', plot_type = 'scatter')

# Display the plot
print(p2)
```

**Interpretation**:

- The scatter plot illustrates the relationship between attack and defense stats.
- Coloring by legendary status helps identify if legendaries have distinct stat distributions.

---

## 8. `predictive_test()`

**Description**: Automated check on classification performance of the `classify_legendary()` function.

### Function Definition

Since the `predictive_test()` function is intended to perform automated testing, we can implement this using the `testthat` framework.

Create a test script named `test-classify_legendary.R` in your `tests/testthat/` directory.

```{r}
# test-classify_legendary.R

library(testthat)
library(dplyr)

test_that("classify_legendary returns a glm object and achieves acceptable accuracy", {
  # Load data
  data <- read.csv("pokemon.csv", stringsAsFactors = FALSE)
  
  # Run the function
  fit <- classify_legendary(data)
  
  # Test that the output is a glm object
  expect_s3_class(fit, "glm")
  
  # Prepare data for prediction
  df <- data %>%
    filter(!is.na(is_legendary)) %>%
    mutate(
      isLegendary = factor(is_legendary, levels = c(0, 1))
    )
  
  # Predict probabilities
  probs <- predict(fit, type = "response")
  
  # Classify based on a threshold (e.g., 0.5)
  predictions <- ifelse(probs > 0.5, 1, 0)
  
  # Calculate accuracy
  accuracy <- mean(predictions == as.numeric(as.character(df$isLegendary)))
  
  # Test that accuracy is above a threshold, e.g., 75%
  expect_gt(accuracy, 0.75)
})
```


**Interpretation**:

- The test checks whether the `classify_legendary()` function returns the correct object type and whether the model achieves acceptable accuracy.
- Ensuring accuracy above a certain threshold validates the model's effectiveness.

---

# Conclusion

With these additional functions, your `PokemonAnalysis` package now includes:

- **`analyze_experience()`**: Analyzes factors influencing experience growth.
- **`egg_steps_factors()`**: Models egg steps based on stats and type.
- **`strength_weakness_table()`**: Summarizes damage multipliers against types.
- **`plot_base_stats()`**: Visualizes distributions of base stats.
- **`predictive_test()`**: Provides automated testing of classification performance.

Each function includes validation steps and visualizations to enhance the analysis and ensure correctness. Remember to:

- **Document** each function properly using `roxygen2` comments.
- **Include Examples** in each function's documentation to guide users.
- **Add Vignettes** demonstrating the use of these functions in real analyses.
- **Ensure Package Compliance** by checking your package with `R CMD check` to avoid errors and warnings.

By completing these functions and their validations, our group package will offer comprehensive tools for analyzing Pokémon data, making it valuable for users interested in data analysis and the Pokémon universe.
